---
title: "Homework Coding 2"
author: "KhoaLe"
date: "02/07/2022"
output:
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tinytex::install_tinytex()
```

# Chapter 6
# Question 6.7.3
**(a)**

```{r}
# Using the isis dataset to the data frame
mydf_iris <- iris

# Grouping label - Coverting to binary 
mydf_iris$binary <- gsub("setosa", "0", mydf_iris$Species)
mydf_iris$binary <- gsub("versicolor", "0", mydf_iris$binary)
mydf_iris$binary <- gsub("virginica", "1", mydf_iris$binary)


# Convert to numeric 
mydf_iris$binary <- as.numeric(mydf_iris$binary)

```

**(b)**

```{r}
# Reading library 
library(splitstackshape)

# Sampling into training and testing 
training_testing_iris <- stratified(as.data.frame(mydf_iris), group = 6, 
                                    size = 0.8, bothSets = T)
# Deleting Species 
df <- subset(mydf_iris, select = -c(Species))

# Building a logistic regression with using all data 
my_logit <- glm(binary ~ Sepal.Length+Sepal.Width+Petal.Length+Petal.Width,
                data = df, family = "binomial")
# Summary my_logit
summary(my_logit)
```
The result of summary my_logit
**(c)**

```{r}
# Calculate the probability
my_prob <- 1/(1+exp(-(-42.638 +-2.465*9 +-6.681*5 + 9.429*10 + 18.286*7)))

# Print result
print(my_prob)

```
Base on the logistic regression model, there will be 100% chance of a new plant
being a Virginca. 


# Question 6.7.4
**(a)**
```{r}
# Reading library 
library(rpart)

# Using the kyphosis dataset to the data frame
mydf_kyphosis <- kyphosis

# Converting variable to numeric 
mydf_kyphosis$binary <- gsub("present", "1", mydf_kyphosis$Kyphosis)
mydf_kyphosis$binary <- gsub("absent", "0", mydf_kyphosis$binary)

# Converting to numeric
mydf_kyphosis$binary <- as.numeric(mydf_kyphosis$binary)
```
**(b)**

```{r}
# Building a logistic regression with using all data 
my_logit1 <- glm(binary ~ Age+Number+Start,
                data = mydf_kyphosis, family = "binomial")
# Summary my_logit
summary(my_logit1)
```

Base on the summary, we have:

- The variables of Age and Number are both insignificant

- Start variable has a great impact on our regression with p-value = 0.00229

**(c)**
```{r}
# Calculate the probability
my_prob1 <- 1/(1+exp(-(-2.036934 + 0.010930*50 + 0.410601*5 + -0.206510*10)))

# Print result
print(my_prob1)
```
Base on the logistic regression model, there will be 18.2% chance of being 
"present" for Age, Start, and Number

# Question 6.7.5
```{r}
# Install package 
#install.packages("lmtest")

#Loading library
library("lmtest")
```
Definition of homoscedastic and heterscedasticity (According to Frost, n.d):
- Heteroscedasticity is a change in the spread of residuals over a range of measured values that is systematic. Because ordinary least squares (OLS) regression implies that all residuals are obtained from a population with a fixed variance, heteroscedasticity is a concern (homoscedasticity).


Note from the book (Kurnicki, n.d): 

- If p-value is lower than 0.5 or 1, we must reject the null hypothesis and 
come to the conclusion that heteroscedasticity exists. 

- The data is homoscedastic, according to the null hypothesis
(error variances are all equal). This is why, in order to conclude 
homoscedasticity, we need larger p-values.



```{r}
# Set x = Sepal.Width, y = Sepal.Length
plot(x= mydf_iris$Sepal.Width, y=mydf_iris$Sepal.Length, type = "p")


```
As a result, this is homoscedastic

```{r}
# Testing for heteroscendasticity by using linear  
# x = Sepal.Width, y = Sepal.Length
swidth_slength <- lm(Sepal.Length~Sepal.Width, data = mydf_iris)
bptest(swidth_slength)
```
The p-value is 0.3764

```{r}
# Set x = Petal.Length, y = Sepal.Length
plot(x= mydf_iris$Petal.Length, y=mydf_iris$Sepal.Length, type = "p")

```
As a result, this is heteroscedastic

```{r}
# Testing for heteroscendasticity by using linear  
# x = Petal.Length, y = Sepal.Length
plength_slength <- lm(Petal.Length~Sepal.Length, data = mydf_iris)
bptest(plength_slength)
```
The p-value is 0.07715


```{r}
# Set x = Petal.Width, y = Sepal.Length
plot(x= mydf_iris$Petal.Width, y=mydf_iris$Sepal.Length, type = "p")

```
As a result, this is heteroscedastic 

```{r}
# Testing for heteroscendasticity by using linear  
# x = Petal.Width, y = Sepal.Length
plength_slength <- lm(Petal.Width~Sepal.Length, data = mydf_iris)
bptest(plength_slength)
```
The p-value is 0.4195 


Reference: 

Frost, J.(n.d). Heteroscedasticity in Regression Analysis. Retrieved on
February 08, 2022. Available at:
https://statisticsbyjim.com/regression/heteroscedasticity-regression/. 

Kurnicki, T.(n.d). Learn R. By coding. 

